---
title: "Industry Equity Cost of Capital"
author: "Mike Aguilar, Bob Connolly, and Jiaxi Li"
output: github_document
always_allow_html: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(warning = FALSE)
```

```{r}
# Packages
library(here)
library(tidyverse)
library(rollRegres)
library(kableExtra)
library(moments)

# Set the function to transform yyyymm to Date
transDate <- function(date) {
  as.Date(
    paste(
      substr(as.character(date),1,4),
      "-",
      substr(as.character(date),5,6),
      "-01",
      sep =""
    )
  )
}

# Create function for STL for tibble based on the ggsdc source code
stl_tibble <- function(data, xvar, yvar, frequency=12, s_window=7, robust = FALSE){
  # xvar and yvar must be characters
  data <- as.data.frame(data, stringsAsFactors = FALSE) # I hate tibbles
  data <- data[order(data[ , xvar]), ]
  y <- ts(data[ , yvar], frequency = frequency)
  model <- stl(y, s.window = s_window, robust = robust)
  y2 <- as.numeric(model$time.series[ , 2])
  y3 <- as.numeric(model$time.series[ , 1])
  y4 <- as.numeric(model$time.series[ , 3])
  
  sdc <- rbind(
    data.frame(data,
               x = data[ , xvar],
               y = as.numeric(y),
               component = "Original")  ,
    data.frame(data,
               x = data[ , xvar],
               y = y2,
               component = "Trend"),
    data.frame(data,
               x = data[ , xvar],
               y = y3,
               component = "Seasonal"),
    data.frame(data,
               x = data[ , xvar],
               y = y4,
               component = "Noise")
  )

  return(sdc)
}
```


## 1. Introduction

In 1997, Fama and French attempted to calculate the equity cost of capital (ECC) for the industry portfolios. They employed the CAPM and Fama French three-factor model and applied various techniques to estimate the factor loadings. The conclusion was the ECC estimation is not reliable due to the imprecise factor risk premium and the uncertain risk loadings. It has been 23 years and we will try to find a possible improvement of the ECC estimation in this paper.

For the model selection, we will apply the Fama French five-factor model (2013) and the PRS five-factor model (2018). Since the five-factor model is an update of the three-factor model, it should work better than the three-factor model. Pukthuanthong et al. (2018) showed that there are 5 factors are reasonable: the market factor, profitability factor, and traded version of credit spread, term spread, and unexpected inflation. We will also use their result to form the Industry Equity Cost of Capital.

We will use the 5-year rolling window to estimate the factor loadings of the ECC. Many other methods such as Bayes shrinkage, and Levi-Welch (2017) method. Levi and Welch tried to estimate the ECC while focusing on the factor exposure estimation and let the reader choose their own methods of expected factor premium. However, we found that the factor risk premiums is the more important piece in ECC estimation. In this paper, we will focus on finding a way to estimate the expected factor premium better.

Many papers mentioned that the expected factor premiums are evolving. We will therefore apply the Fama Macbeth (1973) method to estimate the expected factor premium. Since the 2nd step regression result is extremely volatile, we will apply the STL filtering to smooth the result.

## 2. Data

We get the monthly industry return, Fama French five-factor, and the risk-free rate for the Fama French five factors data from the [Ken French Data Library](https://mba.tuck.dartmouth.edu/pages/faculty/ken.french/data_library.html). The market factor and profitability factor of the PRS five factors are from the Fama French five factors. The other 3 traded macro factors and risk-free rates are extracted from the [Federal Reserve Bank of St. Louis Economic Data (FRED)](https://fred.stlouisfed.org/) and constructed based on Pukthuanthong et al. (2018).

### 2.1 Industry Return and Fama French Five Factors

The [Fama French Five Factors](https://mba.tuck.dartmouth.edu/pages/faculty/ken.french/data_library.html) are simple returns from July 1963 to June 2020. They are as follows: Rm-Rf, SMB, HML, RMW, CMA. The 49 Industry Portfolios are value-weighted simple returns July 1926 to June 2020. The 49 Industry Portfolios without any missing values started in July 1969, so we will start the analysis in July 1969. The risk-free rate is one-month Treasury bill rate.

```{r, eval = FALSE}
# This will only ran once to grab the raw data and process the data
    # Download the return and Fama French 5 Factors data from Ken French Data Library
    # Create temp_file to store the file
    temp_file1 <- tempfile()
    
    # Download the file
    download.file('https://mba.tuck.dartmouth.edu/pages/faculty/ken.french/ftp/F-F_Research_Data_5_Factors_2x3_CSV.zip', temp_file1)
    
    # Unzip the file, to extract the data
    ff_factors_raw_data <- unzip(temp_file1, exdir = here("data"))
    
    
    # Create temp_file to store the file
    temp_file2 <- tempfile()
    
    # Download the file
    download.file('https://mba.tuck.dartmouth.edu/pages/faculty/ken.french/ftp/49_Industry_Portfolios_CSV.zip', temp_file2)
    
    # Unzip the file, to extract the data
    IP49_raw_data <- unzip(temp_file2, exdir = here("data"))
```

```{r, cache = TRUE}
    # Read the contents read_csv
    FF5 <- read_csv(here("data/F-F_Research_Data_5_Factors_2x3.CSV"), skip = 3) %>%
      mutate_all(as.numeric) %>%
      rename(date = X1) %>%
      filter(date >196300) %>%
      # Change all the returns into decimals
      mutate_at(vars(-date), function(x, na.rm = FALSE) (x/100)) %>%
      mutate(date = as.character(date))

    # Read the contents read_csv and extract the desired dates
    Portfolios <- read_csv(here("data/49_Industry_Portfolios.CSV"), skip = 11) %>%
      mutate_all(as.numeric) %>%
      rename(date = X1) %>%
      filter(date > 192600) %>%
      # Change all the returns into decimals
      mutate_at(vars(-date), function(x, na.rm = FALSE) (x/100)) %>%
      mutate(date = as.character(date))
    
    # Keep Value Weighted
    Portfolios <- Portfolios[1:(nrow(Portfolios)/4),]
    Portfolios <- Portfolios %>%
      # remove missing value
      replace(. < -.999, NA) %>%
      remove_missing() %>%
      # Gather all the returns
      gather(Industry, RET, - date)
```

### 2.2 Traded PRS Five Factors

In order to construct the traded version of PRS Factor, we first obtain the risk-free rate and the raw CRR Five Factors: the Default Premium (dDP), the Industrial Production Growth Rate (dIP), the Term Premium (dTS), the Unexpected Inflation (UNEXPI), and the Change in Expected Inflation (dEI). We obtained following macro variables from the Federal Reserve Bank of St. Louis Economic Data: [Moody's Seasoned Aaa Corporate Bond Yield (Aaa)](https://fred.stlouisfed.org/series/AAA), [Moody's Seasoned Baa Corporate Bond Yield (Baa)](https://fred.stlouisfed.org/series/BAA), [Industrial Production Index (IP)](https://fred.stlouisfed.org/series/INDPRO), [10-Year Treasury Constant Maturity Rate (GS10)](https://fred.stlouisfed.org/series/GS10), [1-Year Treasury Constant Maturity Rate (GS1)](https://fred.stlouisfed.org/series/GS1), [Seasonally Adjusted CPI derived Inflation Rate (INF)](https://fred.stlouisfed.org/series/CPIAUCSL), [University of Michigan Inflation Expectation (MICH)](https://fred.stlouisfed.org/series/MICH), [3-Month Treasury Bill: Secondary Market Rate (TB3MS)](https://fred.stlouisfed.org/series/TB3MS).

Here are the ways that the raw factors are calculated:

$$dDP_{raw,t} = Baa_t - Aaa_t$$

$$dIP_{raw, t} = ln(IP_t) - ln(IP_{t-1})$$

$$dTS_{raw, t} = GS10_t - GS1_t$$

$$EXPINF_{raw, t} = E_{t-12}[MICH_t]$$

$$UNEXPI_{raw, t} = INF_t - EXPINF_{raw, t}$$

$$dEI_t = EXPINF_{raw, t} - EXPINF_{raw, t-1}$$

The Default Premium started in Janurary 1919; the Industrial Production Growth Rate stared in Feburary 1919; the Term Premium started in April 1953; the Unexpected Inflation started in Janurary 1979; and the Change in Expected Inflation started in Feburary 1979; 3-Month Treasury Bill: Secondary Market Rate (TB3MS) started in Janurary 1934. Therefore, the raw PRS factors would start in Feburary 1979. The Default Premium (dDP), the Term Premium (dTS), the Unexpected Inflation (UNEXPI), the Change in Expected Inflation (dEI), and 3-month Treasury Rate are annual rates so they need to be converted to monthly frequency.

After obtaining the raw factors, we need to create the traded version of these 5 factors. Similar to the Pukthuanthong et al. (2018) procedure, we applied the 50 portfolios, $R$, (the ten equal-weighted size portfolios, ten equal-weighted book-to-market portfolios, ten equal-weighted investment portfolios and ten equal-weighted operating profitability portfolios, and ten value-weighted momentum portfolios) from the [Ken French Data Library](https://mba.tuck.dartmouth.edu/pages/faculty/ken.french/data_library.html) to construct the mimicking portfolios. These 50 portfolios all exist after July 1963. We first regress each of the 50 assets against the raw factors to get the coefficient matrix B (50x5) and the diagonal matrix of the covariance matrix of the error term V (50x50). The weight of the factor mimicking portfolio is $w=(B'V^{-1}B)^{-1}B'V^{-1}$. The traded factors are PRS = wR, and they would start in July 1963.

```{r, eval = FALSE}
library(data.table)

# Create function to change "yyyy-mm-dd" to yyyymm
antitransDate <- function(date) {
  floor(
    as.numeric(gsub("[^[:digit:]]", "", date))/100
  )
}

# Create function to change "yyyy-mm-dd" to yyyymmdd
antitransDate_daily <- function(date) {
  round(
    as.numeric(gsub("[^[:digit:]]", "", date, perl = TRUE))
  )
}


# Set the Start Date
start_date <- "1900-01-01"
start_date_lead <- as.Date(as.character(antitransDate_daily(start_date)-20000), "%Y%m%d")
end_date <- Sys.Date()

## Load the data from FRED
# Download the dDP (default spread) from FRED, Baa - Aaa, adjust to monthly frequency
dDP_raw <- fread(paste("https://fred.stlouisfed.org/graph/fredgraph.csv?bgcolor=%23e1e9f0&chart_type=line&drp=0&fo=open%20sans&graph_bgcolor=%23ffffff&height=450&mode=fred&recession_bars=on&txtcolor=%23444444&ts=12&tts=12&width=1168&nt=0&thu=0&trc=0&show_legend=yes&show_axis_titles=yes&show_tooltip=yes&id=BAA_AAA&scale=left&cosd=", start_date, "&coed=", Sys.Date(), "&line_color=%234572a7&link_values=false&line_style=solid&mark_type=none&mw=3&lw=2&ost=-99999&oet=99999&mma=0&fml=a-b&fq=Monthly&fam=avg&fgst=lin&fgsnd=", Sys.Date(), "&line_index=1&transformation=lin_lin&vintage_date=", Sys.Date(), "_", Sys.Date(), "&revision_date=", Sys.Date(), "_", Sys.Date(), "&nd=1919-01-01_1919-01-01", sep = "")) %>%
  rename(dDP = BAA_AAA) %>%
  mutate(dDP = (exp(log(1+dDP/100)/12)-1)*100)

# Download the IP (Industrial Production Index) from FRED, times 100 to have the percent change
dIP_raw <- fread(paste("https://fred.stlouisfed.org/graph/fredgraph.csv?bgcolor=%23e1e9f0&chart_type=line&drp=0&fo=open%20sans&graph_bgcolor=%23ffffff&height=450&mode=fred&recession_bars=on&txtcolor=%23444444&ts=12&tts=12&width=1168&nt=0&thu=0&trc=0&show_legend=yes&show_axis_titles=yes&show_tooltip=yes&id=INDPRO&scale=left&cosd=", start_date_lead, "&coed=", Sys.Date(), "&line_color=%234572a7&link_values=false&line_style=solid&mark_type=none&mw=3&lw=2&ost=-99999&oet=99999&mma=0&fml=a&fq=Monthly&fam=avg&fgst=lin&fgsnd=", Sys.Date(), "&line_index=1&transformation=lin&vintage_date=", Sys.Date(), "&revision_date=", Sys.Date(), "&nd=1919-01-01", sep = "")) %>%
  mutate(dIP = log(INDPRO) - log(lag(INDPRO))) %>%
  subset(select = c(DATE, dIP)) %>%
  mutate(dIP = 100*dIP)

# Download the dTS (term spread) from FRED
dTS_raw <- fread(paste("https://fred.stlouisfed.org/graph/fredgraph.csv?bgcolor=%23e1e9f0&chart_type=line&drp=0&fo=open%20sans&graph_bgcolor=%23ffffff&height=450&mode=fred&recession_bars=on&txtcolor=%23444444&ts=12&tts=12&width=1168&nt=0&thu=0&trc=0&show_legend=yes&show_axis_titles=yes&show_tooltip=yes&id=GS10_GS1&scale=left&cosd=", start_date, "&coed=", Sys.Date(), "&line_color=%234572a7&link_values=false&line_style=solid&mark_type=none&mw=3&lw=2&ost=-99999&oet=99999&mma=0&fml=a-b&fq=Monthly&fam=avg&fgst=lin&fgsnd=", Sys.Date(), "&line_index=1&transformation=lin_lin&vintage_date=", Sys.Date(), "_", Sys.Date(), "&revision_date=", Sys.Date(), "_", Sys.Date(), "&nd=1953-04-01_1953-04-01", sep = "")) %>%
  rename(dTS = GS10_GS1) %>%
  mutate(dTS = (exp(log(1+dTS/100)/12)-1)*100)

# Download the Inflation Rate and Expected Inflation Rate
INF_raw <- fread(paste("https://fred.stlouisfed.org/graph/fredgraph.csv?bgcolor=%23e1e9f0&chart_type=line&drp=0&fo=open%20sans&graph_bgcolor=%23ffffff&height=450&mode=fred&recession_bars=on&txtcolor=%23444444&ts=12&tts=12&width=1168&nt=0&thu=0&trc=0&show_legend=yes&show_axis_titles=yes&show_tooltip=yes&id=CPIAUCSL&scale=left&cosd=", start_date, "&coed=", Sys.Date(), "&line_color=%234572a7&link_values=false&line_style=solid&mark_type=none&mw=3&lw=2&ost=-99999&oet=99999&mma=0&fml=a&fq=Monthly&fam=avg&fgst=lin&fgsnd=", Sys.Date(), "&line_index=1&transformation=pc1&vintage_date=", Sys.Date(), "&revision_date=", Sys.Date(), "&nd=1913-01-01", sep = ""))
EXPINF_raw <- fread(paste("https://fred.stlouisfed.org/graph/fredgraph.csv?bgcolor=%23e1e9f0&chart_type=line&drp=0&fo=open%20sans&graph_bgcolor=%23ffffff&height=450&mode=fred&recession_bars=on&txtcolor=%23444444&ts=12&tts=12&width=1168&nt=0&thu=0&trc=0&show_legend=yes&show_axis_titles=yes&show_tooltip=yes&id=MICH&scale=left&cosd=", start_date_lead, "&coed=", Sys.Date(), "&line_color=%234572a7&link_values=false&line_style=solid&mark_type=none&mw=3&lw=2&ost=-99999&oet=99999&mma=0&fml=a&fq=Monthly&fam=avg&fgst=lin&fgsnd=", Sys.Date(), "&line_index=1&transformation=lin&vintage_date=", Sys.Date(), "&revision_date=", Sys.Date(), "&nd=1978-01-01", sep = ""))
EXPINF_raw_lead <- EXPINF_raw %>%
  mutate(MICH = lag(MICH,12))

# Create unexpected inflation
UNEXPI_raw <- INF_raw %>%
  inner_join(EXPINF_raw_lead) %>%
  mutate(UNEXPI = CPIAUCSL_PC1 - MICH) %>%
  subset(select = c(DATE, UNEXPI)) %>%
  mutate(UNEXPI = (exp(log(1+UNEXPI/100)/12)-1)*100)

# Create the change in expected inflation
dEI_raw <- EXPINF_raw_lead %>%
  mutate(dEI = MICH - lag(MICH)) %>%
  subset(select = c(DATE, dEI)) %>%
  mutate(dEI = (exp(log(1+dEI/100)/12)-1)*100)

# Download the 3-month yield as the risk free rate
RF_monthly <- fread(paste("https://fred.stlouisfed.org/graph/fredgraph.csv?bgcolor=%23e1e9f0&chart_type=line&drp=0&fo=open%20sans&graph_bgcolor=%23ffffff&height=450&mode=fred&recession_bars=on&txtcolor=%23444444&ts=12&tts=12&width=1168&nt=0&thu=0&trc=0&show_legend=yes&show_axis_titles=yes&show_tooltip=yes&id=TB3MS&scale=left&cosd=", start_date, "&coed=", Sys.Date(), "&line_color=%234572a7&link_values=false&line_style=solid&mark_type=none&mw=3&lw=2&ost=-99999&oet=99999&mma=0&fml=a&fq=Monthly&fam=avg&fgst=lin&fgsnd=", Sys.Date(),"&line_index=1&transformation=lin&vintage_date=", Sys.Date(), "&revision_date=", Sys.Date(), "&nd=1934-01-01", sep = "")) %>%
  rename(RF = TB3MS) %>%
  mutate(RF = (exp(log(1+RF/100)/12)-1)*100)


# Create the 5 raw CRR factors
CRR_raw <- dDP_raw %>%
  inner_join(dIP_raw) %>%
  inner_join(dTS_raw) %>%
  inner_join(UNEXPI_raw) %>%
  inner_join(dEI_raw) %>%
  inner_join(RF_monthly) %>%
  mutate(DATE = antitransDate(DATE)) %>%
  remove_missing()


##################################################
##################################################
# Monthly mimicking portfolios data
# Create temp_file to store the file
temp_file3 <- tempfile()
temp_file4 <- tempfile()
temp_file5 <- tempfile()
temp_file6 <- tempfile()
temp_file7 <- tempfile()

# Download the file
download.file('https://mba.tuck.dartmouth.edu/pages/faculty/ken.french/ftp/Portfolios_Formed_on_ME_CSV.zip', temp_file3)
download.file('https://mba.tuck.dartmouth.edu/pages/faculty/ken.french/ftp/Portfolios_Formed_on_BE-ME_CSV.zip', temp_file4)
download.file('https://mba.tuck.dartmouth.edu/pages/faculty/ken.french/ftp/Portfolios_Formed_on_OP_CSV.zip', temp_file5)
download.file('https://mba.tuck.dartmouth.edu/pages/faculty/ken.french/ftp/Portfolios_Formed_on_INV_CSV.zip', temp_file6)
download.file('https://mba.tuck.dartmouth.edu/pages/faculty/ken.french/ftp/10_Portfolios_Prior_12_2_CSV.zip', temp_file7)

# Unzip the file, to extract the data
Portfolios_Formed_on_ME_raw_data <- unzip(temp_file3, exdir = here("data"))
Portfolios_Formed_on_BE_ME_raw_data <- unzip(temp_file4, exdir = here("data"))
Portfolios_Formed_on_OP_raw_data <- unzip(temp_file5, exdir = here("data"))
Portfolios_Formed_on_INV_raw_data <- unzip(temp_file6, exdir = here("data"))
Portfolios_Formed_on_MOM_raw_data <- unzip(temp_file7, exdir = here("data"))

# Read the contents read_csv and extract the desired dates
Portfolios_Formed_on_ME <- read_csv(Portfolios_Formed_on_ME_raw_data, skip = 12) %>%
  mutate_all(as.numeric) %>%
  filter(X1 >= antitransDate(start_date),
         X1 <= antitransDate(Sys.Date())) %>%
  rename(DATE = X1)

Portfolios_Formed_on_BE_ME <- read_csv(Portfolios_Formed_on_BE_ME_raw_data, skip = 23) %>%
  mutate_all(as.numeric) %>%
  filter(X1 >= antitransDate(start_date),
         X1 <= antitransDate(Sys.Date())) %>%
  rename(DATE = X1)

Portfolios_Formed_on_OP <- read_csv(Portfolios_Formed_on_OP_raw_data, skip = 24) %>%
  mutate_all(as.numeric) %>%
  filter(X1 >= antitransDate(start_date),
         X1 <= antitransDate(Sys.Date())) %>%
  rename(DATE = X1)

Portfolios_Formed_on_INV <- read_csv(Portfolios_Formed_on_INV_raw_data, skip = 17) %>%
  mutate_all(as.numeric) %>%
  filter(X1 >= antitransDate(start_date),
         X1 <= antitransDate(Sys.Date())) %>%
  rename(DATE = X1)

Portfolios_Formed_on_MOM <- read_csv(Portfolios_Formed_on_MOM_raw_data, skip = 10) %>%
  mutate_all(as.numeric) %>%
  filter(X1 >= antitransDate(start_date),
         X1 <= antitransDate(Sys.Date())) %>%
  rename(DATE = X1)

# Keep only the equal-weighted ones except equal-weighted MOM
Portfolios_Formed_on_ME <- Portfolios_Formed_on_ME[(nrow(Portfolios_Formed_on_ME)/4+1):(nrow(Portfolios_Formed_on_ME)/2),c(1,11:20)]
Portfolios_Formed_on_BE_ME <- Portfolios_Formed_on_BE_ME[(nrow(Portfolios_Formed_on_BE_ME)/4+1):(nrow(Portfolios_Formed_on_BE_ME)/2),c(1,11:20)]
Portfolios_Formed_on_OP <- Portfolios_Formed_on_OP[(nrow(Portfolios_Formed_on_OP)/4+1):(nrow(Portfolios_Formed_on_OP)/2),c(1,10:19)]
Portfolios_Formed_on_INV <- Portfolios_Formed_on_INV[(nrow(Portfolios_Formed_on_INV)/4+1):(nrow(Portfolios_Formed_on_INV)/2),c(1,10:19)]
Portfolios_Formed_on_MOM <- Portfolios_Formed_on_MOM[(1:(nrow(Portfolios_Formed_on_MOM)/4)),]

# Select and rename the portfolios
names(Portfolios_Formed_on_ME)[2:11]<- paste(rep("ME",10),1:10,sep = "")
names(Portfolios_Formed_on_BE_ME)[2:11]<- paste(rep("BE_ME",10),1:10,sep = "")
names(Portfolios_Formed_on_OP)[2:11]<- paste(rep("OP",10),1:10,sep = "")
names(Portfolios_Formed_on_INV)[2:11]<- paste(rep("INV",10),1:10,sep = "")
names(Portfolios_Formed_on_MOM)[2:11]<- paste(rep("MOM",10),1:10,sep = "")

# Join the 50 decile portfolios together
D50 <- Portfolios_Formed_on_ME %>%
  inner_join(Portfolios_Formed_on_BE_ME) %>%
  inner_join(Portfolios_Formed_on_OP) %>%
  inner_join(Portfolios_Formed_on_INV) %>%
  inner_join(Portfolios_Formed_on_MOM) %>%
  mutate(DATE = as.numeric(DATE))

##################################################
##################################################
# Use the monthly raw data and 50 portfolios to create the weights
reg_table <- D50
names(reg_table)[2:51] <- 1:50
reg_table <- reg_table %>%
  pivot_longer(-DATE, names_to = "port", values_to = "RET") %>%
  filter(DATE <= antitransDate(end_date)) %>%
  inner_join(CRR_raw) %>%
  subset(select = - RF) %>%
  mutate(port = as.numeric(port)) %>%
  ungroup()

# Do the regression
B_temp <- reg_table %>%
  group_by(port) %>%
  do(model = lm(RET ~ . - port - DATE, data = .) %>%
       coefficients())

V_temp <- reg_table %>%
  group_by(port) %>%
  do(model = lm(RET ~ . - port - DATE, data = .) %>%
       resid())

# Unwrap the results
B <- do.call(rbind.data.frame, B_temp$model) %>%
  as.matrix()
B <- B[,2:ncol(B)]
# rename B
colnames(B) <- names(CRR_raw)[2:(length(CRR_raw)-1)]

V <- do.call(rbind.data.frame, V_temp$model) %>%
  as.matrix() %>%
  t() %>%
  cov() %>%
  diag() %>%
  diag()

# Calculate the weights
w <- solve(t(B) %*% solve(V) %*% B) %*% t(B) %*% solve(V)


##################################################
##################################################
# Create the monthly traded version of CRR factors
CRR_trade_monthly <- t(w %*% t(D50[,2:51])) %>%
  as_tibble()
CRR_trade_monthly <- cbind(D50[,1], CRR_trade_monthly)

# Create the PRS monthly factor file
PRS_monthly <- FF5 %>%
  subset(select = c(date, `Mkt-RF`, RMW)) %>%
  mutate_at(vars(-date), function(x, na.rm = FALSE) (x*100)) %>%
  rename(DATE = date) %>%
  mutate(DATE = as.numeric(DATE)) %>%
  inner_join(CRR_trade_monthly) %>% 
  inner_join(RF_monthly %>%
               mutate(DATE = antitransDate(DATE))) %>%
  subset(select = -c(dEI, dIP)) %>%
  rename(date = DATE) %>%
  mutate(date = as.character(date))
  
# save as csv
write.csv(PRS_monthly, here("data/PRS_monthly.csv"), na = "",  row.names = FALSE)
```

```{r, cache = TRUE}
    # Read the contents read_csv
    PRS <- read_csv(here("data/PRS_monthly.csv")) %>%
      mutate_all(as.numeric) %>%
      filter(date >196300) %>%
      # Change all the returns into decimals
      mutate_at(vars(-date), function(x, na.rm = FALSE) (x/100)) %>%
      mutate(date = as.character(date))
```

## 3. First-Pass Regression

In this section, we will try to apply the simple first-pass regression to estimate the betas of the 49 industry portfolios. The period would be from July 1969 to June 2020. Since the focus of this paper is about the factor risk premium estimation, we will use the most basic first pass regressions (full sample and 5-year rolling window) to estimate the betas and compare which lamdba method would work better.

### 3.1 Fama French Five Factor Model

We will first apply the Fama French Five Factor Model to estimate the betas. We will use the Five Factor Model as the base model.

### 3.1.1 Full Sample Estimation
```{r, cache = TRUE}
# We will perform the simple first step regression here
# Join the portfolios and FF5
Port_FF5 <- Portfolios %>%      
  inner_join(FF5) %>%
  # Create Risk Premium as RP
  rename(RP = RET) %>%
  mutate(RP = RP - RF) %>%
  # Get rid of RF
  subset(select = -RF) %>%
  # Change date back to numeric
  mutate(date = as.integer(date)) %>%
  # Locate the time and asset when 5-year rolling beta is possible to estimate (59 entries before, the PERMNO is the same, the date is 4 year 11 month less)
  mutate(Selection = (Industry == lag(Industry,59)) & ((date == (lag(date,59)+411))|(date == lag(date,59)+499)),
         Selection = replace_na(Selection,FALSE))

# Calculate the full sample betas
# Create the IDs for Industry
Ind_ID <- Port_FF5 %>%
  group_by(Industry) %>%
  summarise(n = n()) %>%
  mutate(Ind_ID = 1:length(unique(Port_FF5$Industry))) %>%
  subset(select = -n)

# apply the full sample regression to calculate the full sample beta for portfolios
temp1 <- Port_FF5 %>%
  subset(select = -Selection) %>%
  inner_join(Ind_ID) %>%
  subset(select = - Industry) %>%
  # unite the Ind_ID
  group_by(Ind_ID) %>%
  do(model = lm(RP ~ . - Ind_ID - date, data = .) %>%
       coefficients())

# Unwrap the results
Port_FF5_Betas_Full <- do.call(rbind.data.frame, temp1$model) %>%
  as_tibble()

# Rename the variables
names(Port_FF5_Betas_Full) = names(FF5)[-length(FF5)]
names(Port_FF5_Betas_Full)[1] = "Alpha"

# Add in the Ind_ID and years, then addin Industry
Port_FF5_Betas_Full <- Ind_ID %>%
  inner_join(cbind(temp1[, 1], Port_FF5_Betas_Full)) %>%
  subset(select = -Ind_ID)

# apply the full sample regression to calculate the full sample beta for portfolios
temp1 <- Port_FF5 %>%
  subset(select = -Selection) %>%
  inner_join(Ind_ID) %>%
  subset(select = - Industry) %>%
  # unite the Ind_ID
  group_by(Ind_ID) %>%
  do(model = lm(RP ~ . - Ind_ID - date, data = .) %>%
       summary() %>%
       .$coefficients %>%
       .[,2])

# Unwrap the results
Port_FF5_Betas_se_Full <- do.call(rbind.data.frame, temp1$model) %>%
  as_tibble()

# Rename the variables
names(Port_FF5_Betas_se_Full) = names(FF5)[-length(FF5)]
names(Port_FF5_Betas_se_Full)[1] = "Alpha"

# Add in the Ind_ID and years, then addin Industry
Port_FF5_Betas_se_Full <- Ind_ID %>%
  inner_join(cbind(temp1[, 1], Port_FF5_Betas_se_Full)) %>%
  subset(select = -Ind_ID)

# Create the table
Port_FF5_Betas_Full %>%
  cbind(Port_FF5_Betas_se_Full[,-1]) %>%
  kable(align = "c", caption = "Fama French Five Factors") %>%
        kable_styling(font_size = 10, "striped", full_width = F) %>%
        column_spec(1, bold = T) %>%
        # Add header above
        add_header_above(c(" " = 1, "Coefficients" = 6, "Std. Error" = 6))

# Plot the histogram for betas
Port_FF5_Betas_Full %>%
  subset(select = -Alpha) %>%
  # pivot longer to make factors a category
  pivot_longer(cols = -Industry,
               names_to = "Factors",
               values_to = "betas") %>%
  # Fix the order of Factors
  mutate(Factors = factor(Factors, level= unique(.$Factors))) %>%
  ggplot(aes(Industry, betas)) +
  geom_bar(stat = "identity") +
  facet_wrap(~ Factors,
             scales = "free") +
  labs(title="Full Sample Betas with Fama French Five Factors") + 
  theme(plot.title = element_text(hjust=0.5),
        plot.subtitle = element_text(hjust = 0.5),
        axis.text.x = element_text(angle = 30, hjust = 1))
```


### 3.1.2 Rolling Window Estimation

We will show an example of the Real Estate Portfolio (RlEst) Rolling Betas evolutions here. The smoothing line is based on the loess smoothing. It seems that the betas are evolving overtime.

```{r, cache = TRUE}
# Create the estimated portfolio beta matrix
Port_FF5_Betas <- Port_FF5 %>%
  rename(Alpha = RP)

# apply the roll_regres to calculate the 5-year rolling beta (60 data points)
temp_out <- roll_regres(RP ~ . -Industry -date -Selection, Port_FF5, width = 60L)
# Save as tibble
temp_betas <- temp_out$coefs %>% as_tibble()

# Assign them to Betas
for (j in 3:(length(Port_FF5_Betas)-1)) {
  Port_FF5_Betas[,j] <- temp_betas[,j-2]
}

# Filter the needed ones and remove Selection
Port_FF5_Betas <- Port_FF5_Betas %>%
  filter(Selection == TRUE) %>%
  subset(select = -Selection)

# Plot the rolling betas
Port_FF5_Betas %>%
  subset(select = -Alpha) %>%
  # Translate the date
  mutate(date = transDate(date)) %>%
  # pivot longer to make factors a category
  pivot_longer(cols = -c(date, Industry),
               names_to = "Factors",
               values_to = "betas") %>%
  filter(Industry == "RlEst") %>%
  # Fix the order of Factors
  mutate(Factors = factor(Factors, level= unique(.$Factors))) %>%
  ggplot(aes(date, betas)) +
  geom_line() +
  # loess method: local regression fitting
  geom_smooth(method = "loess") +
  scale_x_date() +
  facet_wrap(~ Factors,
             scales = "free") +
  labs(title= "Estimated 5-year Rolling Betas with Fama French Five Factors for RlEst",
       x = "date", y = "betas") +
  scale_x_date(minor_breaks = "1 year") +
  theme(plot.title = element_text(hjust=0.5),
        axis.text.x = element_text(angle = 75, hjust = 1))
```

### 3.1.3 Full Sample Estimation with STL Trend

Here, we would try to conduct the STL decomposition before the first step regression with full sample.

```{r, cache = TRUE}
# STL method with s_window = 7, no robust weight
Port_STL_s7_norobust <- Port_FF5 %>%
  subset(select = c(date, Industry, RP)) %>%
  group_by(Industry) %>%
  do(model = stl_tibble(., "date", "RP")) %>%
  .$model %>%
  do.call(what = rbind.data.frame)

FF5_STL_s7_norobust <- FF5 %>%
  subset(select = -RF) %>%
  mutate(date = as.numeric(date)) %>%
  pivot_longer(cols = -date, names_to = "Factors", values_to = "Values") %>%
  # Fix the order of Factors
  mutate(Factors = factor(Factors, level= unique(.$Factors))) %>%
  group_by(Factors) %>%
  do(model = stl_tibble(., "date", "Values")) %>%
  .$model %>%
  do.call(what = rbind.data.frame) %>%
  filter(component == "Trend") %>%
  subset(select = -c(Values, x, component)) %>%
  pivot_wider(names_from = "Factors", values_from = "y")

# apply the full sample regression to calculate the full sample beta for portfolios
temp1 <- Port_STL_s7_norobust %>%
  filter(component == "Trend") %>%
  subset(select = -c(RP, x, component)) %>%
  rename(RP = y) %>%
  inner_join(FF5_STL_s7_norobust) %>%
  inner_join(Ind_ID) %>%
  subset(select = - Industry) %>%
  # unite the Ind_ID
  group_by(Ind_ID) %>%
  do(model = lm(RP ~ . - Ind_ID - date, data = .) %>%
       coefficients())

# Unwrap the results
Port_FF5_STL_Betas_Full <- do.call(rbind.data.frame, temp1$model) %>%
  as_tibble()

# Rename the variables
names(Port_FF5_STL_Betas_Full) = names(FF5)[-length(FF5)]
names(Port_FF5_STL_Betas_Full)[1] = "Alpha"

# Add in the Ind_ID and years, then addin Industry
Port_FF5_STL_Betas_Full <- Ind_ID %>%
  inner_join(cbind(temp1[, 1], Port_FF5_STL_Betas_Full)) %>%
  subset(select = -Ind_ID)

# apply the full sample regression to calculate the full sample beta for portfolios
temp1 <- Port_STL_s7_norobust %>%
  filter(component == "Trend") %>%
  subset(select = -c(RP, x, component)) %>%
  rename(RP = y) %>%
  inner_join(FF5_STL_s7_norobust) %>%
  inner_join(Ind_ID) %>%
  subset(select = - Industry) %>%
  # unite the Ind_ID
  group_by(Ind_ID) %>%
  do(model = lm(RP ~ . - Ind_ID - date, data = .) %>%
       summary() %>%
       .$coefficients %>%
       .[,2])

# Unwrap the results
Port_FF5_STL_Betas_se_Full <- do.call(rbind.data.frame, temp1$model) %>%
  as_tibble()

# Rename the variables
names(Port_FF5_STL_Betas_se_Full) = names(FF5)[-length(FF5)]
names(Port_FF5_STL_Betas_se_Full)[1] = "Alpha"

# Add in the Ind_ID and years, then addin Industry
Port_FF5_STL_Betas_se_Full <- Ind_ID %>%
  inner_join(cbind(temp1[, 1], Port_FF5_STL_Betas_se_Full)) %>%
  subset(select = -Ind_ID)

# Create the table
Port_FF5_STL_Betas_Full %>%
  cbind(Port_FF5_STL_Betas_se_Full[,-1]) %>%
  kable(align = "c", caption = "Fama French Five Factors") %>%
        kable_styling(font_size = 10, "striped", full_width = F) %>%
        column_spec(1, bold = T) %>%
        # Add header above as % Equity
        add_header_above(c(" " = 1, "Coefficients" = 6, "Std. Error" = 6))

# Plot the histogram for betas
Port_FF5_STL_Betas_Full %>%
  subset(select = -Alpha) %>%
  # pivot longer to make factors a category
  pivot_longer(cols = -Industry,
               names_to = "Factors",
               values_to = "betas") %>%
  # Fix the order of Factors
  mutate(Factors = factor(Factors, level= unique(.$Factors))) %>%
  ggplot(aes(Industry, betas)) +
  geom_bar(stat = "identity") +
  facet_wrap(~ Factors,
             scales = "free") +
  labs(title="Full Sample STL Betas with Fama French Five Factors") + 
  theme(plot.title = element_text(hjust=0.5),
        plot.subtitle = element_text(hjust = 0.5),
        axis.text.x = element_text(angle = 30, hjust = 1))
```

### 3.1.4 Rolling Window Estimation with STL Trend

Here, we would try to conduct the STL decomposition before the first step regression with full sample.

```{r, cache = TRUE}
  # Locate the time and asset when 5-year rolling beta is possible to estimate (59 entries before, the PERMNO is the same, the date is 4 year 11 month less)
temp <- Port_STL_s7_norobust %>%
  filter(component == "Trend") %>%
  subset(select = -c(RP, x, component)) %>%
  rename(RP = y) %>%
  inner_join(FF5_STL_s7_norobust) %>%
  mutate(Selection = (Industry == lag(Industry,59)) & ((date == (lag(date,59)+411))|(date == lag(date,59)+499)),
         Selection = replace_na(Selection,FALSE))

# Create the estimated portfolio beta matrix
Port_FF5_STL_Betas <- temp %>%
  rename(Alpha = RP)

# apply the roll_regres to calculate the 5-year rolling beta (60 data points)
temp_out <- roll_regres(RP ~ . -Industry -date -Selection, temp, width = 60L)
# Save as tibble
temp_betas <- temp_out$coefs %>% as_tibble()

# Assign them to Betas
for (j in 3:(length(Port_FF5_STL_Betas)-1)) {
  Port_FF5_STL_Betas[,j] <- temp_betas[,j-2]
}

# Filter the needed ones and remove Selection
Port_FF5_STL_Betas <- Port_FF5_STL_Betas %>%
  filter(Selection == TRUE) %>%
  subset(select = -Selection)

# Plot the rolling betas
Port_FF5_STL_Betas %>%
  subset(select = -Alpha) %>%
  # Translate the date
  mutate(date = transDate(date)) %>%
  # pivot longer to make factors a category
  pivot_longer(cols = -c(date, Industry),
               names_to = "Factors",
               values_to = "betas") %>%
  filter(Industry == "RlEst") %>%
  # Fix the order of Factors
  mutate(Factors = factor(Factors, level= unique(.$Factors))) %>%
  ggplot(aes(date, betas)) +
  geom_line() +
  # loess method: local regression fitting
  geom_smooth(method = "loess") +
  scale_x_date() +
  facet_wrap(~ Factors,
             scales = "free") +
  labs(title= "Estimated 5-year Rolling STL Betas with Fama French Five Factors for RlEst",
       x = "date", y = "betas") +
  scale_x_date(minor_breaks = "1 year") +
  theme(plot.title = element_text(hjust=0.5),
        axis.text.x = element_text(angle = 75, hjust = 1))
```


### 3.2 PRS Five Factor Model

We will then apply the PRS Five Factor Model to estimate the betas.

### 3.2.1 Full Sample Estimation
```{r, cache = TRUE}
# We will perform the simple first step regression here
# Join the portfolios and PRS
Port_PRS <- Portfolios %>%      
  inner_join(PRS) %>%
  # Create Risk Premium as RP
  rename(RP = RET) %>%
  mutate(RP = RP - RF) %>%
  # Get rid of RF
  subset(select = -RF) %>%
  # Change date back to numeric
  mutate(date = as.integer(date)) %>%
  # Locate the time and asset when 5-year rolling beta is possible to estimate (59 entries before, the PERMNO is the same, the date is 4 year 11 month less)
  mutate(Selection = (Industry == lag(Industry,59)) & ((date == (lag(date,59)+411))|(date == lag(date,59)+499)),
         Selection = replace_na(Selection,FALSE))

# apply the full sample regression to calculate the full sample beta for portfolios
temp1 <- Port_PRS %>%
  subset(select = -Selection) %>%
  inner_join(Ind_ID) %>%
  subset(select = - Industry) %>%
  # unite the Ind_ID
  group_by(Ind_ID) %>%
  do(model = lm(RP ~ . - Ind_ID - date, data = .) %>%
       coefficients())

# Unwrap the results
Port_PRS_Betas_Full <- do.call(rbind.data.frame, temp1$model) %>%
  as_tibble()

# Rename the variables
names(Port_PRS_Betas_Full) = names(PRS)[-length(PRS)]
names(Port_PRS_Betas_Full)[1] = "Alpha"

# Add in the Ind_ID and years, then addin Industry
Port_PRS_Betas_Full <- Ind_ID %>%
  inner_join(cbind(temp1[, 1], Port_PRS_Betas_Full)) %>%
  subset(select = -Ind_ID)

# apply the full sample regression to calculate the full sample beta for portfolios
temp1 <- Port_PRS %>%
  subset(select = -Selection) %>%
  inner_join(Ind_ID) %>%
  subset(select = - Industry) %>%
  # unite the Ind_ID
  group_by(Ind_ID) %>%
  do(model = lm(RP ~ . - Ind_ID - date, data = .) %>%
       summary() %>%
       .$coefficients %>%
       .[,2])

# Unwrap the results
Port_PRS_Betas_se_Full <- do.call(rbind.data.frame, temp1$model) %>%
  as_tibble()

# Rename the variables
names(Port_PRS_Betas_se_Full) = names(PRS)[-length(PRS)]
names(Port_PRS_Betas_se_Full)[1] = "Alpha"

# Add in the Ind_ID and years, then addin Industry
Port_PRS_Betas_se_Full <- Ind_ID %>%
  inner_join(cbind(temp1[, 1], Port_PRS_Betas_se_Full)) %>%
  subset(select = -Ind_ID)

# Create the table
Port_PRS_Betas_Full %>%
  cbind(Port_PRS_Betas_se_Full[,-1]) %>%
  kable(align = "c", caption = "PRS Five Factors") %>%
  kable_styling(font_size = 10, "striped", full_width = F) %>%
  column_spec(1, bold = T) %>%
  # Add header above as % Equity
  add_header_above(c(" " = 1, "Coefficients" = 6, "Std. Error" = 6))

# Plot the histogram for betas
Port_PRS_Betas_Full %>%
  subset(select = -Alpha) %>%
  # pivot longer to make factors a category
  pivot_longer(cols = -Industry,
               names_to = "Factors",
               values_to = "betas") %>%
  # Fix the order of Factors
  mutate(Factors = factor(Factors, level= unique(.$Factors))) %>%
  ggplot(aes(Industry, betas)) +
  geom_bar(stat = "identity") +
  facet_wrap(~ Factors,
             scales = "free") +
  labs(title="Full Sample Betas with PRS Five Factors") + 
  theme(plot.title = element_text(hjust=0.5),
        plot.subtitle = element_text(hjust = 0.5),
        axis.text.x = element_text(angle = 30, hjust = 1))
```


### 3.2.2 Rolling Window Estimation

We will show an example of the Real Estate Portfolio (RlEst) Rolling Betas evolutions here. The smoothing line is based on the loess smoothing. It seems that the betas are evolving overtime.

```{r, cache = TRUE}
# Create the estimated portfolio beta matrix
Port_PRS_Betas <- Port_PRS %>%
  rename(Alpha = RP)

# apply the roll_regres to calculate the 5-year rolling beta (60 data points)
temp_out <- roll_regres(RP ~ . -Industry -date -Selection, Port_PRS, width = 60L)
# Save as tibble
temp_betas <- temp_out$coefs %>% as_tibble()

# Assign them to Betas
for (j in 3:(length(Port_PRS_Betas)-1)) {
  Port_PRS_Betas[,j] <- temp_betas[,j-2]
}

# Filter the needed ones and remove Selection
Port_PRS_Betas <- Port_PRS_Betas %>%
  filter(Selection == TRUE) %>%
  subset(select = -Selection)

# Plot the rolling betas
Port_PRS_Betas %>%
  subset(select = -Alpha) %>%
  # Translate the date
  mutate(date = transDate(date)) %>%
  # pivot longer to make factors a category
  pivot_longer(cols = -c(date, Industry),
               names_to = "Factors",
               values_to = "betas") %>%
  filter(Industry == "RlEst") %>%
  # Fix the order of Factors
  mutate(Factors = factor(Factors, level= unique(.$Factors))) %>%
  ggplot(aes(date, betas)) +
  geom_line() +
  # loess method: local regression fitting
  geom_smooth(method = "loess") +
  scale_x_date() +
  facet_wrap(~ Factors,
             scales = "free") +
  labs(title= "Estimated 5-year Rolling Betas with PRS Five Factors for RlEst",
       x = "date", y = "betas") +
  scale_x_date(minor_breaks = "1 year") +
  theme(plot.title = element_text(hjust=0.5),
        axis.text.x = element_text(angle = 75, hjust = 1))
```

### 3.2.3 Full Sample Estimation with STL Trend

Here, we would try to conduct the STL decomposition before the first step regression with full sample.

```{r, cache = TRUE}
# STL method with s_window = 7, no robust weight
PRS_STL_s7_norobust <- PRS %>%
  subset(select = -RF) %>%
  mutate(date = as.numeric(date)) %>%
  pivot_longer(cols = -date, names_to = "Factors", values_to = "Values") %>%
  # Fix the order of Factors
  mutate(Factors = factor(Factors, level= unique(.$Factors))) %>%
  group_by(Factors) %>%
  do(model = stl_tibble(., "date", "Values")) %>%
  .$model %>%
  do.call(what = rbind.data.frame) %>%
  filter(component == "Trend") %>%
  subset(select = -c(Values, x, component)) %>%
  pivot_wider(names_from = "Factors", values_from = "y")

# apply the full sample regression to calculate the full sample beta for portfolios
temp1 <- Port_STL_s7_norobust %>%
  filter(component == "Trend") %>%
  subset(select = -c(RP, x, component)) %>%
  rename(RP = y) %>%
  inner_join(PRS_STL_s7_norobust) %>%
  inner_join(Ind_ID) %>%
  subset(select = - Industry) %>%
  # unite the Ind_ID
  group_by(Ind_ID) %>%
  do(model = lm(RP ~ . - Ind_ID - date, data = .) %>%
       coefficients())

# Unwrap the results
Port_PRS_STL_Betas_Full <- do.call(rbind.data.frame, temp1$model) %>%
  as_tibble()

# Rename the variables
names(Port_PRS_STL_Betas_Full) = names(PRS)[-length(PRS)]
names(Port_PRS_STL_Betas_Full)[1] = "Alpha"

# Add in the Ind_ID and years, then addin Industry
Port_PRS_STL_Betas_Full <- Ind_ID %>%
  inner_join(cbind(temp1[, 1], Port_PRS_STL_Betas_Full)) %>%
  subset(select = -Ind_ID)

# apply the full sample regression to calculate the full sample beta for portfolios
temp1 <- Port_STL_s7_norobust %>%
  filter(component == "Trend") %>%
  subset(select = -c(RP, x, component)) %>%
  rename(RP = y) %>%
  inner_join(PRS_STL_s7_norobust) %>%
  inner_join(Ind_ID) %>%
  subset(select = - Industry) %>%
  # unite the Ind_ID
  group_by(Ind_ID) %>%
  do(model = lm(RP ~ . - Ind_ID - date, data = .) %>%
       summary() %>%
       .$coefficients %>%
       .[,2])

# Unwrap the results
Port_PRS_STL_Betas_se_Full <- do.call(rbind.data.frame, temp1$model) %>%
  as_tibble()

# Rename the variables
names(Port_PRS_STL_Betas_se_Full) = names(PRS)[-length(PRS)]
names(Port_PRS_STL_Betas_se_Full)[1] = "Alpha"

# Add in the Ind_ID and years, then addin Industry
Port_PRS_STL_Betas_se_Full <- Ind_ID %>%
  inner_join(cbind(temp1[, 1], Port_PRS_STL_Betas_se_Full)) %>%
  subset(select = -Ind_ID)

# Create the table
Port_PRS_STL_Betas_Full %>%
  cbind(Port_PRS_STL_Betas_se_Full[,-1]) %>%
  kable(align = "c", caption = "PRS Five Factors") %>%
  kable_styling(font_size = 10, "striped", full_width = F) %>%
  column_spec(1, bold = T) %>%
  # Add header above as % Equity
  add_header_above(c(" " = 1, "Coefficients" = 6, "Std. Error" = 6))

# Plot the histogram for betas
Port_PRS_STL_Betas_Full %>%
  subset(select = -Alpha) %>%
  # pivot longer to make factors a category
  pivot_longer(cols = -Industry,
               names_to = "Factors",
               values_to = "betas") %>%
  # Fix the order of Factors
  mutate(Factors = factor(Factors, level= unique(.$Factors))) %>%
  ggplot(aes(Industry, betas)) +
  geom_bar(stat = "identity") +
  facet_wrap(~ Factors,
             scales = "free") +
  labs(title="Full Sample STL Betas with PRS Five Factors") + 
  theme(plot.title = element_text(hjust=0.5),
        plot.subtitle = element_text(hjust = 0.5),
        axis.text.x = element_text(angle = 30, hjust = 1))
```

### 3.2.4 Rolling Window Estimation with STL Trend

Here, we would try to conduct the STL decomposition before the first step regression with full sample.

```{r, cache = TRUE}
# Locate the time and asset when 5-year rolling beta is possible to estimate (59 entries before, the PERMNO is the same, the date is 4 year 11 month less)
temp <- Port_STL_s7_norobust %>%
  filter(component == "Trend") %>%
  subset(select = -c(RP, x, component)) %>%
  rename(RP = y) %>%
  inner_join(PRS_STL_s7_norobust) %>%
  mutate(Selection = (Industry == lag(Industry,59)) & ((date == (lag(date,59)+411))|(date == lag(date,59)+499)),
         Selection = replace_na(Selection,FALSE))

# Create the estimated portfolio beta matrix
Port_PRS_STL_Betas <- temp %>%
  rename(Alpha = RP)

# apply the roll_regres to calculate the 5-year rolling beta (60 data points)
temp_out <- roll_regres(RP ~ . -Industry -date -Selection, temp, width = 60L)
# Save as tibble
temp_betas <- temp_out$coefs %>% as_tibble()

# Assign them to Betas
for (j in 3:(length(Port_PRS_STL_Betas)-1)) {
  Port_PRS_STL_Betas[,j] <- temp_betas[,j-2]
}

# Filter the needed ones and remove Selection
Port_PRS_STL_Betas <- Port_PRS_STL_Betas %>%
  filter(Selection == TRUE) %>%
  subset(select = -Selection)

# Plot the rolling betas
Port_PRS_STL_Betas %>%
  subset(select = -Alpha) %>%
  # Translate the date
  mutate(date = transDate(date)) %>%
  # pivot longer to make factors a category
  pivot_longer(cols = -c(date, Industry),
               names_to = "Factors",
               values_to = "betas") %>%
  filter(Industry == "RlEst") %>%
  # Fix the order of Factors
  mutate(Factors = factor(Factors, level= unique(.$Factors))) %>%
  ggplot(aes(date, betas)) +
  geom_line() +
  # loess method: local regression fitting
  geom_smooth(method = "loess") +
  scale_x_date() +
  facet_wrap(~ Factors,
             scales = "free") +
  labs(title= "Estimated 5-year Rolling STL Betas with PRS Five Factors for RlEst",
       x = "date", y = "betas") +
  scale_x_date(minor_breaks = "1 year") +
  theme(plot.title = element_text(hjust=0.5),
        axis.text.x = element_text(angle = 75, hjust = 1))
```

It seems that the STL decomposition does not help the first step regression.

## 4. Factor Premium Estimation

In this section, we will describe different ways to estimate the Factor Premium.

### 4.1 Arithmetic Mean

First, one can take the arithmetic mean of the factors to generate the expected factor premium.

```{r, cache = TRUE}
AM_FF5 <- FF5 %>%
  subset(select = -date) %>%
  summarise_all(mean)

AM_PRS <- PRS %>%
  subset(select = -date) %>%
  summarise_all(mean)
```


### 4.2 Geometric Mean

Levi and Welch mentioned in their 2017 paper that geometric mean might perform better. So in this section, we will calculate the geometric mean as the factor premium. 

```{r, cache = TRUE}
GM_FF5 <- FF5 %>%
  subset(select = -date) %>%
  summarise_all(function(x, na.rm = FALSE) (exp(mean(log(1+x)))-1))

GM_PRS <- PRS %>%
  subset(select = -date) %>%
  summarise_all(function(x, na.rm = FALSE) (exp(mean(log(1+x)))-1))
```

### 4.3 Fama Macbeth Second Step Regression

Fama-Macbeth second regression estimated lambda represents the expected factor risk premium. In this section, we will apply the second step regression to estimate the factor risk premium.

```{r, cache = TRUE}
# Fama Macbeth method
# With Fama French Five Factors
# Create the second-path portfolio for estimation lambda
Second_Path <- Port_FF5 %>%
  subset(select = c(date, Industry, RP)) %>%
  inner_join(Port_FF5_Betas) %>%
  subset(select = -Alpha) %>%
  ungroup()

# Group the data and do the second pass regression
Rolling_Second <- Second_Path %>%
  group_by(date) %>%
  do(model = lm(RP ~ . - date - Industry, data = .) %>%
       coefficients())

# Unwrap the results
Rolling_Lambdas <- do.call(rbind.data.frame, Rolling_Second$model) %>%
  as_tibble()

# Rename the variables
names(Rolling_Lambdas) = names(FF5)[-length(FF5)]
names(Rolling_Lambdas)[1] = "Lambda0"

# Add in the dates
FM_FF5 <- cbind(Rolling_Second[, 1], Rolling_Lambdas) %>%
  subset(select = -Lambda0)

# Plot the FM_FF5
FM_FF5 %>%
  pivot_longer(cols = -date, names_to = "Factors", values_to = "RP") %>%
  # Fix the order of Factors
  mutate(Factors = factor(Factors, level= unique(.$Factors))) %>%
  mutate(date = transDate(date)) %>%
  ggplot(aes(date, RP, group = Factors)) +
  geom_line() +
  scale_x_date() +
  facet_wrap(~ Factors,
             scales = "free") +
  labs(title= "Estimated Expected Fama French Five Factors Premium with Fama Macbeth Method",
       x = "date", y = "Lambda") +
  scale_x_date(minor_breaks = "1 year") +
  theme(plot.title = element_text(hjust=0.5),
        axis.text.x = element_text(angle = 75, hjust = 1))
  

# With PRS Five Factors
# Create the second-path portfolio for estimation lambda
Second_Path <- Port_PRS %>%
  subset(select = c(date, Industry, RP)) %>%
  inner_join(Port_PRS_Betas) %>%
  subset(select = -Alpha) %>%
  ungroup()

# Group the data and do the second pass regression
Rolling_Second <- Second_Path %>%
  group_by(date) %>%
  do(model = lm(RP ~ . - date - Industry, data = .) %>%
       coefficients())

# Unwrap the results
Rolling_Lambdas <- do.call(rbind.data.frame, Rolling_Second$model) %>%
  as_tibble()

# Rename the variables
names(Rolling_Lambdas) = names(PRS)[-length(PRS)]
names(Rolling_Lambdas)[1] = "Lambda0"

# Add in the dates
FM_PRS <- cbind(Rolling_Second[, 1], Rolling_Lambdas) %>%
  subset(select = -Lambda0)

# Plot the FM_PRS
FM_PRS %>%
  pivot_longer(cols = -date, names_to = "Factors", values_to = "RP") %>%
  # Fix the order of Factors
  mutate(Factors = factor(Factors, level= unique(.$Factors))) %>%
  mutate(date = transDate(date)) %>%
  ggplot(aes(date, RP, group = Factors)) +
  geom_line() +
  scale_x_date() +
  facet_wrap(~ Factors,
             scales = "free") +
  labs(title= "Estimated Expected PRS Five Factors Premium with Fama Macbeth Method",
       x = "date", y = "Lambda") +
  scale_x_date(minor_breaks = "1 year") +
  theme(plot.title = element_text(hjust=0.5),
        axis.text.x = element_text(angle = 75, hjust = 1))
```

### 4.4 Fama Macbeth Second Step Regression with STL Deseaoned Data

As we can see, Fama Macbeth method would generate an evolving time-series of factor risk premium, but the volatility in lambda is unreasonablly large. We will try to apply the STL trend in the second step regression to smooth the lambda.

There is no need for trend extraction for 1st step regression, no matter if we use the full sample or rolling window. The window should be large enough to mitgate the seasonality effect. The second step regression, however, is a cross sectional regression. A seasonal component in the time series would disrupt the cross-sectional regression significantly. So it is possible the the large volatility observed in the second step regression is due to the seasonality.

STL method (Cleveland et al. 1990) would try decompose the time-series into 3 components: trend, seaonality, and noise. It applies an iterative smoothing method to extract the trend and seaonality components. At the same time, one can choose to use a robust weighting scheme to reduce the effect of large noise to the trend and seaonality extraction.

We will extract the trend of risk premium of the industry portfolios and the trend of the betas with the STL method, and then conduct the second step regression. There are two options with the STL method: the loess window for seasonal extraction (s_window, large value means no rapidly evolving seasonal component, needs to be odd and at least 7) and robust weights for noise (downweight the noisy data in smoothing if non-Gaussian behavior in the time-series leads to extreme, transient variation). We will first show the STL decomposition of betas and returns.

```{r, cache = TRUE}
# First extract the STL decomposition for industrial returns
# STL method with s_window = 7, no robust weight
Port_STL_s7_norobust <- Port_FF5 %>%
  subset(select = c(date, Industry, RP)) %>%
  group_by(Industry) %>%
  do(model = stl_tibble(., "date", "RP")) %>%
  .$model %>%
  do.call(what = rbind.data.frame)


# STL method with s_window = 7, with robust weight
Port_STL_s7_robust <- Port_FF5 %>%
  subset(select = c(date, Industry, RP)) %>%
  group_by(Industry) %>%
  do(model = stl_tibble(., "date", "RP", robust = TRUE)) %>%
  .$model %>%
  do.call(what = rbind.data.frame)

# STL method with s_window = 15, no robust weight
Port_STL_s15_norobust <- Port_FF5 %>%
  subset(select = c(date, Industry, RP)) %>%
  group_by(Industry) %>%
  do(model = stl_tibble(., "date", "RP", s_window = 15)) %>%
  .$model %>%
  do.call(what = rbind.data.frame)

# STL method with s_window = 15, with robust weight
Port_STL_s15_robust <- Port_FF5 %>%
  subset(select = c(date, Industry, RP)) %>%
  group_by(Industry) %>%
  do(model = stl_tibble(., "date", "RP", s_window = 15, robust = TRUE)) %>%
  .$model %>%
  do.call(what = rbind.data.frame)

# Plot these results for RlEst
Port_STL_s7_norobust %>%
  mutate(date = transDate(date)) %>%
  filter(Industry == "RlEst") %>%
  ggplot(aes(date, y)) +
  geom_line() +
  geom_line() +
  scale_x_date() +
  facet_wrap(~ component,
             ncol = 1,
             scales = "free") +
  labs(title= "STL Decomposition of RlEst Risk Premium",
       subtitle = "s_window = 7 and no robust weigting",
       x = "date", y = "RP") +
  scale_x_date(minor_breaks = "1 year") +
  theme(plot.title = element_text(hjust=0.5),
        plot.subtitle = element_text(hjust=0.5),
        axis.text.x = element_text(angle = 75, hjust = 1))

Port_STL_s7_robust %>%
  mutate(date = transDate(date)) %>%
  filter(Industry == "RlEst") %>%
  ggplot(aes(date, y)) +
  geom_line() +
  geom_line() +
  scale_x_date() +
  facet_wrap(~ component,
             ncol = 1,
             scales = "free") +
  labs(title= "STL Decomposition of RlEst Risk Premium",
       subtitle = "s_window = 7 and robust weigting",
       x = "date", y = "RP") +
  scale_x_date(minor_breaks = "1 year") +
  theme(plot.title = element_text(hjust=0.5),
        plot.subtitle = element_text(hjust=0.5),
        axis.text.x = element_text(angle = 75, hjust = 1))

Port_STL_s15_norobust %>%
  mutate(date = transDate(date)) %>%
  filter(Industry == "RlEst") %>%
  ggplot(aes(date, y)) +
  geom_line() +
  geom_line() +
  scale_x_date() +
  facet_wrap(~ component,
             ncol = 1,
             scales = "free") +
  labs(title= "STL Decomposition of RlEst Risk Premium",
       subtitle = "s_window = 15 and no robust weigting",
       x = "date", y = "RP") +
  scale_x_date(minor_breaks = "1 year") +
  theme(plot.title = element_text(hjust=0.5),
        plot.subtitle = element_text(hjust=0.5),
        axis.text.x = element_text(angle = 75, hjust = 1))

Port_STL_s15_robust %>%
  mutate(date = transDate(date)) %>%
  filter(Industry == "RlEst") %>%
  ggplot(aes(date, y)) +
  geom_line() +
  geom_line() +
  scale_x_date() +
  facet_wrap(~ component,
             ncol = 1,
             scales = "free") +
  labs(title= "STL Decomposition of RlEst Risk Premium",
       subtitle = "s_window = 15 and robust weigting",
       x = "date", y = "RP") +
  scale_x_date(minor_breaks = "1 year") +
  theme(plot.title = element_text(hjust=0.5),
        plot.subtitle = element_text(hjust=0.5),
        axis.text.x = element_text(angle = 75, hjust = 1))
```

The robustness weighting seems not be appropriate for the Industry Risk Premiums since the returns vairation are mostly caused by Gaussian behavior. One example is the end of the trend curve: there was a market crash at the beginning of 2020, so the trend should go down. However, with the robust weighting, the market crash was given little wight and disappeared. At the same time, we might just choose s_window = 7, since there could be changing seasonal patterns in the short-term.

```{r, cache = TRUE}
# FF5 betas STL decomposition
# STL method with s_window = 7, no robust weight
FF5_Betas_STL_s7_norobust <- Port_FF5_Betas %>%
  subset(select = -Alpha) %>%
  pivot_longer(cols = -c(date, Industry), names_to = "Factors", values_to = "Betas") %>%
  group_by(Industry, Factors) %>%
  do(model = stl_tibble(., "date", "Betas")) %>%
  .$model %>%
  do.call(what = rbind.data.frame)

# STL method with s_window = 7, with robust weight
FF5_Betas_STL_s7_robust <- Port_FF5_Betas %>%
  subset(select = -Alpha) %>%
  pivot_longer(cols = -c(date, Industry), names_to = "Factors", values_to = "Betas") %>%
  group_by(Industry, Factors) %>%
  do(model = stl_tibble(., "date", "Betas", robust = TRUE)) %>%
  .$model %>%
  do.call(what = rbind.data.frame)

# STL method with s_window = 15, no robust weight
FF5_Betas_STL_s15_norobust <- Port_FF5_Betas %>%
  subset(select = -Alpha) %>%
  pivot_longer(cols = -c(date, Industry), names_to = "Factors", values_to = "Betas") %>%
  group_by(Industry, Factors) %>%
  do(model = stl_tibble(., "date", "Betas", s_window = 15)) %>%
  .$model %>%
  do.call(what = rbind.data.frame)

# STL method with s_window = 15, with robust weight
FF5_Betas_STL_s15_robust <- Port_FF5_Betas %>%
  subset(select = -Alpha) %>%
  pivot_longer(cols = -c(date, Industry), names_to = "Factors", values_to = "Betas") %>%
  group_by(Industry, Factors) %>%
  do(model = stl_tibble(., "date", "Betas", s_window = 15, robust = TRUE)) %>%
  .$model %>%
  do.call(what = rbind.data.frame)

# Plot these results for RlEst
FF5_Betas_STL_s7_norobust %>%
  mutate(date = transDate(date)) %>%
  filter(Industry == "RlEst") %>%
  # Fix the order of factors
  mutate(Factors = factor(Factors, level= names(FF5)[2:6])) %>%
  ggplot(aes(date, y, color = Factors)) +
  geom_line() +
  geom_line() +
  scale_x_date() +
  facet_wrap(~ component,
             ncol = 1,
             scales = "free") +
  labs(title= "STL Decomposition of RlEst Fama French Five Factor Betas",
       subtitle = "s_window = 7 and no robust weigting",
       x = "date", y = "Betas") +
  scale_x_date(minor_breaks = "1 year") +
  theme(plot.title = element_text(hjust=0.5),
        plot.subtitle = element_text(hjust=0.5),
        axis.text.x = element_text(angle = 75, hjust = 1))

FF5_Betas_STL_s7_robust %>%
  mutate(date = transDate(date)) %>%
  filter(Industry == "RlEst") %>%
  # Fix the order of factors
  mutate(Factors = factor(Factors, level= names(FF5)[2:6])) %>%
  ggplot(aes(date, y, color = Factors)) +
  geom_line() +
  geom_line() +
  scale_x_date() +
  facet_wrap(~ component,
             ncol = 1,
             scales = "free") +
  labs(title= "STL Decomposition of RlEst Fama French Five Factor Betas",
       subtitle = "s_window = 7 and robust weigting",
       x = "date", y = "Betas") +
  scale_x_date(minor_breaks = "1 year") +
  theme(plot.title = element_text(hjust=0.5),
        plot.subtitle = element_text(hjust=0.5),
        axis.text.x = element_text(angle = 75, hjust = 1))

FF5_Betas_STL_s15_norobust %>%
  mutate(date = transDate(date)) %>%
  filter(Industry == "RlEst") %>%
  # Fix the order of factors
  mutate(Factors = factor(Factors, level= names(FF5)[2:6])) %>%
  ggplot(aes(date, y, color = Factors)) +
  geom_line() +
  geom_line() +
  scale_x_date() +
  facet_wrap(~ component,
             ncol = 1,
             scales = "free") +
  labs(title= "STL Decomposition of RlEst Fama French Five Factor Betas",
       subtitle = "s_window = 15 and no robust weigting",
       x = "date", y = "Betas") +
  scale_x_date(minor_breaks = "1 year") +
  theme(plot.title = element_text(hjust=0.5),
        plot.subtitle = element_text(hjust=0.5),
        axis.text.x = element_text(angle = 75, hjust = 1))

FF5_Betas_STL_s15_robust %>%
  mutate(date = transDate(date)) %>%
  filter(Industry == "RlEst") %>%
  # Fix the order of factors
  mutate(Factors = factor(Factors, level= names(FF5)[2:6])) %>%
  ggplot(aes(date, y, color = Factors)) +
  geom_line() +
  geom_line() +
  scale_x_date() +
  facet_wrap(~ component,
             ncol = 1,
             scales = "free") +
  labs(title= "STL Decomposition of RlEst Fama French Five Factor Betas",
       subtitle = "s_window = 15 and robust weigting",
       x = "date", y = "Betas") +
  scale_x_date(minor_breaks = "1 year") +
  theme(plot.title = element_text(hjust=0.5),
        plot.subtitle = element_text(hjust=0.5),
        axis.text.x = element_text(angle = 75, hjust = 1))

# PRS betas STL decomposition
# STL method with s_window = 7, no robust weight
PRS_Betas_STL_s7_norobust <- Port_PRS_Betas %>%
  subset(select = -Alpha) %>%
  pivot_longer(cols = -c(date, Industry), names_to = "Factors", values_to = "Betas") %>%
  group_by(Industry, Factors) %>%
  do(model = stl_tibble(., "date", "Betas")) %>%
  .$model %>%
  do.call(what = rbind.data.frame)

# STL method with s_window = 7, with robust weight
PRS_Betas_STL_s7_robust <- Port_PRS_Betas %>%
  subset(select = -Alpha) %>%
  pivot_longer(cols = -c(date, Industry), names_to = "Factors", values_to = "Betas") %>%
  group_by(Industry, Factors) %>%
  do(model = stl_tibble(., "date", "Betas", robust = TRUE)) %>%
  .$model %>%
  do.call(what = rbind.data.frame)

# STL method with s_window = 15, no robust weight
PRS_Betas_STL_s15_norobust <- Port_PRS_Betas %>%
  subset(select = -Alpha) %>%
  pivot_longer(cols = -c(date, Industry), names_to = "Factors", values_to = "Betas") %>%
  group_by(Industry, Factors) %>%
  do(model = stl_tibble(., "date", "Betas", s_window = 15)) %>%
  .$model %>%
  do.call(what = rbind.data.frame)

# STL method with s_window = 15, with robust weight
PRS_Betas_STL_s15_robust <- Port_PRS_Betas %>%
  subset(select = -Alpha) %>%
  pivot_longer(cols = -c(date, Industry), names_to = "Factors", values_to = "Betas") %>%
  group_by(Industry, Factors) %>%
  do(model = stl_tibble(., "date", "Betas", s_window = 15, robust = TRUE)) %>%
  .$model %>%
  do.call(what = rbind.data.frame)

# Plot these results for RlEst
PRS_Betas_STL_s7_norobust %>%
  mutate(date = transDate(date)) %>%
  filter(Industry == "RlEst") %>%
  # Fix the order of factors
  mutate(Factors = factor(Factors, level= names(PRS)[2:6])) %>%
  ggplot(aes(date, y, color = Factors)) +
  geom_line() +
  geom_line() +
  scale_x_date() +
  facet_wrap(~ component,
             ncol = 1,
             scales = "free") +
  labs(title= "STL Decomposition of RlEst PRS Five Factor Betas",
       subtitle = "s_window = 7 and no robust weigting",
       x = "date", y = "Betas") +
  scale_x_date(minor_breaks = "1 year") +
  theme(plot.title = element_text(hjust=0.5),
        plot.subtitle = element_text(hjust=0.5),
        axis.text.x = element_text(angle = 75, hjust = 1))

PRS_Betas_STL_s7_robust %>%
  mutate(date = transDate(date)) %>%
  filter(Industry == "RlEst") %>%
  # Fix the order of factors
  mutate(Factors = factor(Factors, level= names(PRS)[2:6])) %>%
  ggplot(aes(date, y, color = Factors)) +
  geom_line() +
  geom_line() +
  scale_x_date() +
  facet_wrap(~ component,
             ncol = 1,
             scales = "free") +
  labs(title= "STL Decomposition of RlEst PRS Five Factor Betas",
       subtitle = "s_window = 7 and robust weigting",
       x = "date", y = "Betas") +
  scale_x_date(minor_breaks = "1 year") +
  theme(plot.title = element_text(hjust=0.5),
        plot.subtitle = element_text(hjust=0.5),
        axis.text.x = element_text(angle = 75, hjust = 1))

PRS_Betas_STL_s15_norobust %>%
  mutate(date = transDate(date)) %>%
  filter(Industry == "RlEst") %>%
  # Fix the order of factors
  mutate(Factors = factor(Factors, level= names(PRS)[2:6])) %>%
  ggplot(aes(date, y, color = Factors)) +
  geom_line() +
  geom_line() +
  scale_x_date() +
  facet_wrap(~ component,
             ncol = 1,
             scales = "free") +
  labs(title= "STL Decomposition of RlEst PRS Five Factor Betas",
       subtitle = "s_window = 15 and no robust weigting",
       x = "date", y = "Betas") +
  scale_x_date(minor_breaks = "1 year") +
  theme(plot.title = element_text(hjust=0.5),
        plot.subtitle = element_text(hjust=0.5),
        axis.text.x = element_text(angle = 75, hjust = 1))

PRS_Betas_STL_s15_robust %>%
  mutate(date = transDate(date)) %>%
  filter(Industry == "RlEst") %>%
  # Fix the order of factors
  mutate(Factors = factor(Factors, level= names(PRS)[2:6])) %>%
  ggplot(aes(date, y, color = Factors)) +
  geom_line() +
  geom_line() +
  scale_x_date() +
  facet_wrap(~ component,
             ncol = 1,
             scales = "free") +
  labs(title= "STL Decomposition of RlEst PRS Five Factor Betas",
       subtitle = "s_window = 15 and robust weigting",
       x = "date", y = "Betas") +
  scale_x_date(minor_breaks = "1 year") +
  theme(plot.title = element_text(hjust=0.5),
        plot.subtitle = element_text(hjust=0.5),
        axis.text.x = element_text(angle = 75, hjust = 1))
```

Beta estimation's noise or seasonal pattern is much smaller than trend so the noise weight or the s_winow does not impact the result as much. We are safe by just using the no robust weighting and s_window = 7 and that would make the left- and right-hand-side of the second step regression treated the same.

Now, we will take the desired no robust weighting, s_window = 7 trend results of the Industry Risk Premium and Betas to estimate the factor risk premium.

```{r, cache = TRUE}
# Estimate the Factor Risk Premium for FF5
## Create the second-path portfolio for estimation lambda
Second_Path <- Port_STL_s7_norobust %>%
  filter(component == "Trend") %>%
  subset(select = c(date, Industry, y)) %>%
  rename(RP = y) %>%
  inner_join(FF5_Betas_STL_s7_norobust %>%
               filter(component == "Trend") %>%
               subset(select = c(date, Industry, Factors, y)) %>%
               rename(Betas = y) %>%
               pivot_wider(names_from = Factors, values_from = Betas) %>%
               # reorder
               .[, c("date", "Industry", names(FF5)[2:6])]) %>%
  ungroup()

# Group the data and do the second pass regression
Rolling_Second <- Second_Path %>%
  group_by(date) %>%
  do(model = lm(RP ~ . - date - Industry, data = .) %>%
       coefficients())

# Unwrap the results
Rolling_Lambdas <- do.call(rbind.data.frame, Rolling_Second$model) %>%
  as_tibble()

# Rename the variables
names(Rolling_Lambdas) = names(FF5)[-length(FF5)]
names(Rolling_Lambdas)[1] = "Lambda0"

# Add in the dates
FM_STL_FF5 <- cbind(Rolling_Second[, 1], Rolling_Lambdas) %>%
  subset(select = -Lambda0)

# Plot the FM_STL_FF5
FM_STL_FF5 %>%
  pivot_longer(cols = -date, names_to = "Factors", values_to = "RP") %>%
  # Fix the order of Factors
  mutate(Factors = factor(Factors, level= unique(.$Factors))) %>%
  mutate(date = transDate(date)) %>%
  ggplot(aes(date, RP, group = Factors)) +
  geom_line() +
  scale_x_date() +
  facet_wrap(~ Factors,
             scales = "free") +
  labs(title= "Estimated Expected Fama French Five Factors Premium with Fama Macbeth Method with STL Trend",
       x = "date", y = "Lambda") +
  scale_x_date(minor_breaks = "1 year") +
  theme(plot.title = element_text(hjust=0.5),
        axis.text.x = element_text(angle = 75, hjust = 1))


# Estimate the Factor Risk Premium for PRS
## Create the second-path portfolio for estimation lambda
Second_Path <- Port_STL_s7_norobust %>%
  filter(component == "Trend") %>%
  subset(select = c(date, Industry, y)) %>%
  rename(RP = y) %>%
  inner_join(PRS_Betas_STL_s7_norobust %>%
               filter(component == "Trend") %>%
               subset(select = c(date, Industry, Factors, y)) %>%
               rename(Betas = y) %>%
               pivot_wider(names_from = Factors, values_from = Betas) %>%
               # reorder
               .[, c("date", "Industry", names(PRS)[2:6])]) %>%
  ungroup()

# Group the data and do the second pass regression
Rolling_Second <- Second_Path %>%
  group_by(date) %>%
  do(model = lm(RP ~ . - date - Industry, data = .) %>%
       coefficients())

# Unwrap the results
Rolling_Lambdas <- do.call(rbind.data.frame, Rolling_Second$model) %>%
  as_tibble()

# Rename the variables
names(Rolling_Lambdas) = names(PRS)[-length(PRS)]
names(Rolling_Lambdas)[1] = "Lambda0"

# Add in the dates
FM_STL_PRS <- cbind(Rolling_Second[, 1], Rolling_Lambdas) %>%
  subset(select = -Lambda0)

# Plot the FM_STL_PRS
FM_STL_PRS %>%
  pivot_longer(cols = -date, names_to = "Factors", values_to = "RP") %>%
  # Fix the order of Factors
  mutate(Factors = factor(Factors, level= unique(.$Factors))) %>%
  mutate(date = transDate(date)) %>%
  ggplot(aes(date, RP, group = Factors)) +
  geom_line() +
  scale_x_date() +
  facet_wrap(~ Factors,
             scales = "free") +
  labs(title= "Estimated Expected PRS Five Factors Premium with Fama Macbeth Method with STL Trend",
       x = "date", y = "Lambda") +
  scale_x_date(minor_breaks = "1 year") +
  theme(plot.title = element_text(hjust=0.5),
        axis.text.x = element_text(angle = 75, hjust = 1))

```

Here is a comparison of the lambda statitics of the Normal Fama Macbeth and Fama Macbeth Second Step Regression with STL Trend Data.

```{r, cache = TRUE}
FF5_table <- FM_FF5 %>%
  summarise_all(mean) %>%
  mutate(date = "mean") %>%
  rbind(FM_FF5 %>%
          summarise_all(var) %>%
          mutate(date = "variance")) %>%
  rbind(FM_FF5 %>%
          summarise_all(skewness) %>%
          mutate(date = "skewness")) %>%
  rbind(FM_FF5 %>%
          summarise_all(kurtosis) %>%
          mutate(date = "kurtosis")) %>%
  rename(stats = date) %>%
  mutate(method = "FM_FF5") %>%
  rbind(FM_STL_FF5 %>%
    summarise_all(mean) %>%
    mutate(date = "mean") %>%
    rbind(FM_STL_FF5 %>%
            summarise_all(var) %>%
            mutate(date = "variance")) %>%
    rbind(FM_STL_FF5 %>%
            summarise_all(skewness) %>%
            mutate(date = "skewness")) %>%
    rbind(FM_STL_FF5 %>%
            summarise_all(kurtosis) %>%
            mutate(date = "kurtosis")) %>%
    rename(stats = date) %>%
    mutate(method = "FM_STL_FF5")) %>%
  subset(select = c(7,1:6)) 

FF5_table %>%
  kable(align = "c", caption = "Fama French Five Factors Lambdas") %>%
  kable_styling(font_size = 10, "striped", full_width = F) %>%
  column_spec(1, bold = T) %>%
  collapse_rows(columns = 1)



PRS_table <- FM_PRS %>%
  summarise_all(mean) %>%
  mutate(date = "mean") %>%
  rbind(FM_PRS %>%
          summarise_all(var) %>%
          mutate(date = "variance")) %>%
  rbind(FM_PRS %>%
          summarise_all(skewness) %>%
          mutate(date = "skewness")) %>%
  rbind(FM_PRS %>%
          summarise_all(kurtosis) %>%
          mutate(date = "kurtosis")) %>%
  rename(stats = date) %>%
  mutate(method = "FM_PRS") %>%
  rbind(FM_STL_PRS %>%
    summarise_all(mean) %>%
    mutate(date = "mean") %>%
    rbind(FM_STL_PRS %>%
            summarise_all(var) %>%
            mutate(date = "variance")) %>%
    rbind(FM_STL_PRS %>%
            summarise_all(skewness) %>%
            mutate(date = "skewness")) %>%
    rbind(FM_STL_PRS %>%
            summarise_all(kurtosis) %>%
            mutate(date = "kurtosis")) %>%
    rename(stats = date) %>%
    mutate(method = "FM_STL_PRS")) %>%
  subset(select = c(7,1:6))

PRS_table %>%
  kable(align = "c", caption = "PRS Five Factors Lambdas") %>%
  kable_styling(font_size = 10, "striped", full_width = F) %>%
  column_spec(1, bold = T) %>%
  collapse_rows(columns = 1)

(FF5_table[2,3:7]/FF5_table[6,3:7]) %>%
  as_tibble() %>%
  cbind((PRS_table[2,3:7]/PRS_table[6,3:7]) %>%
          as_tibble()) %>%
  kable(align = "c", caption = "Fama Macbeth/STL Lambda Variance Ratio") %>%
  kable_styling(font_size = 10, "striped", full_width = F) %>%
  # Add header above
  add_header_above(c("FF5" = 5, "PRS" = 5))


```

## 5. Equity Cost of Captial

### 5.1 Estimated Equity Cost of Captial

As the equation indicates, $ECC = \sum_{i \in F} \beta_i*E[F_i] + R_f$. We will ignore the risk free rate part and the Equity Cost of Capital in this section refers to the estimated risk premium. 

### 5.1.1 Arithmetic Mean

```{r, cache = TRUE}
# Create an id to join data
temp <- AM_FF5 %>%
  mutate(id=1)
names(temp) <- tolower(names(temp))
# create id and join
temp <- Port_FF5_Betas %>%
  mutate(id=1) %>%
  inner_join(temp) %>%
  subset(select = -c(Alpha, id, rf))

# Calculate the ECC 
ECC_AM_FF5 <- temp[,1:2] %>%
  cbind(temp[,3:7]*temp[,8:12]) %>%
  mutate(ECC = rowSums(.[3:7]))

# Decompose the ECC: Beta, Lambda, and Projection Parameter
ECC_AM_FF5_Norms <- cbind(sqrt(rowSums(temp[,3:7]^2)),sqrt(rowSums(temp[,8:12]^2))) %>%
  as_tibble() %>%
  rename(Betas = V1,
         Lambdas = V2) %>%
  cbind(ECC_AM_FF5) %>%
  subset(select = c(Industry, date, ECC, Betas, Lambdas)) %>%
  mutate(PP = ECC/Betas/Lambdas,
         ECC = abs(ECC),
         PP = abs(PP)) %>%
  # transform to ln
  mutate(ECC = log(ECC),
         Betas = log(Betas)/ECC,
         Lambdas = log(Lambdas)/ECC,
         PP = log(PP)/ECC) %>%
  subset(select = - ECC) %>%
  # pivot longer
  pivot_longer(cols = c(Betas, Lambdas, PP), names_to = "Component", values_to = "Percent")

# Plot the ECC_AM_FF5
ECC_AM_FF5 %>%
  mutate(date = transDate(date)) %>%
  ggplot(aes(date, ECC)) +
  geom_line() +
  scale_x_date(minor_breaks = "1 year") +
  facet_wrap(~ Industry) +
  labs(title= "Estimated Equity Cost of Capital with AM_FF5",
       x = "date") + 
  theme(plot.title = element_text(hjust=0.5),
        axis.text.x = element_text(angle = 30, hjust = 1))


# Create an id to join data
temp <- AM_PRS %>%
  mutate(id=1)
names(temp) <- tolower(names(temp))
# create id and join
temp <- Port_PRS_Betas %>%
  mutate(id=1) %>%
  inner_join(temp) %>%
  subset(select = -c(Alpha, id, rf))

# Calculate the ECC 
ECC_AM_PRS <- temp[,1:2] %>%
  cbind(temp[,3:7]*temp[,8:12]) %>%
  mutate(ECC = rowSums(.[3:7]))

# Decompose the ECC: Beta, Lambda, and Projection Parameter
ECC_AM_PRS_Norms <- cbind(sqrt(rowSums(temp[,3:7]^2)),sqrt(rowSums(temp[,8:12]^2))) %>%
  as_tibble() %>%
  rename(Betas = V1,
         Lambdas = V2) %>%
  cbind(ECC_AM_PRS) %>%
  subset(select = c(Industry, date, ECC, Betas, Lambdas)) %>%
  mutate(PP = ECC/Betas/Lambdas,
         ECC = abs(ECC),
         PP = abs(PP)) %>%
  # transform to ln
  mutate(ECC = log(ECC),
         Betas = log(Betas)/ECC,
         Lambdas = log(Lambdas)/ECC,
         PP = log(PP)/ECC) %>%
  subset(select = - ECC) %>%
  # pivot longer
  pivot_longer(cols = c(Betas, Lambdas, PP), names_to = "Component", values_to = "Percent")

# Plot the ECC_AM_PRS
ECC_AM_PRS %>%
  mutate(date = transDate(date)) %>%
  ggplot(aes(date, ECC)) +
  geom_line() +
  scale_x_date(minor_breaks = "1 year") +
  facet_wrap(~ Industry) +
  labs(title= "Estimated Equity Cost of Capital with AM_PRS",
       x = "date") + 
  theme(plot.title = element_text(hjust=0.5),
        axis.text.x = element_text(angle = 30, hjust = 1))
```

### 5.1.2 Geometric Mean

```{r, cache = TRUE}
# Create an id to join data
temp <- GM_FF5 %>%
  mutate(id=1)
names(temp) <- tolower(names(temp))
# create id and join
temp <- Port_FF5_Betas %>%
  mutate(id=1) %>%
  inner_join(temp) %>%
  subset(select = -c(Alpha, id, rf))

# Calculate the ECC 
ECC_GM_FF5 <- temp[,1:2] %>%
  cbind(temp[,3:7]*temp[,8:12]) %>%
  mutate(ECC = rowSums(.[3:7]))

# Decompose the ECC: Beta, Lambda, and Projection Parameter
ECC_GM_FF5_Norms <- cbind(sqrt(rowSums(temp[,3:7]^2)),sqrt(rowSums(temp[,8:12]^2))) %>%
  as_tibble() %>%
  rename(Betas = V1,
         Lambdas = V2) %>%
  cbind(ECC_GM_FF5) %>%
  subset(select = c(Industry, date, ECC, Betas, Lambdas)) %>%
  mutate(PP = ECC/Betas/Lambdas,
         ECC = abs(ECC),
         PP = abs(PP)) %>%
  # transform to ln
  mutate(ECC = log(ECC),
         Betas = log(Betas)/ECC,
         Lambdas = log(Lambdas)/ECC,
         PP = log(PP)/ECC) %>%
  subset(select = - ECC) %>%
  # pivot longer
  pivot_longer(cols = c(Betas, Lambdas, PP), names_to = "Component", values_to = "Percent")

# Plot the ECC_GM_FF5
ECC_GM_FF5 %>%
  mutate(date = transDate(date)) %>%
  ggplot(aes(date, ECC)) +
  geom_line() +
  scale_x_date(minor_breaks = "1 year") +
  facet_wrap(~ Industry) +
  labs(title= "Estimated Equity Cost of Capital with GM_FF5",
       x = "date") + 
  theme(plot.title = element_text(hjust=0.5),
        axis.text.x = element_text(angle = 30, hjust = 1))


# Create an id to join data
temp <- GM_PRS %>%
  mutate(id=1)
names(temp) <- tolower(names(temp))
# create id and join
temp <- Port_PRS_Betas %>%
  mutate(id=1) %>%
  inner_join(temp) %>%
  subset(select = -c(Alpha, id, rf))

# Calculate the ECC 
ECC_GM_PRS <- temp[,1:2] %>%
  cbind(temp[,3:7]*temp[,8:12]) %>%
  mutate(ECC = rowSums(.[3:7]))

# Decompose the ECC: Beta, Lambda, and Projection Parameter
ECC_GM_PRS_Norms <- cbind(sqrt(rowSums(temp[,3:7]^2)),sqrt(rowSums(temp[,8:12]^2))) %>%
  as_tibble() %>%
  rename(Betas = V1,
         Lambdas = V2) %>%
  cbind(ECC_GM_PRS) %>%
  subset(select = c(Industry, date, ECC, Betas, Lambdas)) %>%
  mutate(PP = ECC/Betas/Lambdas,
         ECC = abs(ECC),
         PP = abs(PP)) %>%
  # transform to ln
  mutate(ECC = log(ECC),
         Betas = log(Betas)/ECC,
         Lambdas = log(Lambdas)/ECC,
         PP = log(PP)/ECC) %>%
  subset(select = - ECC) %>%
  # pivot longer
  pivot_longer(cols = c(Betas, Lambdas, PP), names_to = "Component", values_to = "Percent")

# Plot the ECC_GM_PRS
ECC_GM_PRS %>%
  mutate(date = transDate(date)) %>%
  ggplot(aes(date, ECC)) +
  geom_line() +
  scale_x_date(minor_breaks = "1 year") +
  facet_wrap(~ Industry) +
  labs(title= "Estimated Equity Cost of Capital with GM_PRS",
       x = "date") + 
  theme(plot.title = element_text(hjust=0.5),
        axis.text.x = element_text(angle = 30, hjust = 1))
```

### 5.1.3 Fama Macbeth Second Step Regression

```{r, cache = TRUE}
temp <- FM_FF5
names(temp) <- tolower(names(temp))
# join the data
temp <- Port_FF5_Betas %>%
  inner_join(temp) %>%
  subset(select = -Alpha)

# Calculate the ECC 
ECC_FM_FF5 <- temp[,1:2] %>%
  cbind(temp[,3:7]*temp[,8:12]) %>%
  mutate(ECC = rowSums(.[3:7]))

# Decompose the ECC: Beta, Lambda, and Projection Parameter
ECC_FM_FF5_Norms <- cbind(sqrt(rowSums(temp[,3:7]^2)),sqrt(rowSums(temp[,8:12]^2))) %>%
  as_tibble() %>%
  rename(Betas = V1,
         Lambdas = V2) %>%
  cbind(ECC_FM_FF5) %>%
  subset(select = c(Industry, date, ECC, Betas, Lambdas)) %>%
  mutate(PP = ECC/Betas/Lambdas,
         ECC = abs(ECC),
         PP = abs(PP)) %>%
  # transform to ln
  mutate(ECC = log(ECC),
         Betas = log(Betas)/ECC,
         Lambdas = log(Lambdas)/ECC,
         PP = log(PP)/ECC) %>%
  subset(select = - ECC) %>%
  # pivot longer
  pivot_longer(cols = c(Betas, Lambdas, PP), names_to = "Component", values_to = "Percent")

# Plot the ECC_FM_FF5
ECC_FM_FF5 %>%
  mutate(date = transDate(date)) %>%
  ggplot(aes(date, ECC)) +
  geom_line() +
  scale_x_date(minor_breaks = "1 year") +
  facet_wrap(~ Industry) +
  labs(title= "Estimated Equity Cost of Capital with FM_FF5",
       x = "date") + 
  theme(plot.title = element_text(hjust=0.5),
        axis.text.x = element_text(angle = 30, hjust = 1))


temp <- FM_PRS
names(temp) <- tolower(names(temp))
# join the data
temp <- Port_PRS_Betas %>%
  inner_join(temp) %>%
  subset(select = -Alpha)

# Calculate the ECC 
ECC_FM_PRS <- temp[,1:2] %>%
  cbind(temp[,3:7]*temp[,8:12]) %>%
  mutate(ECC = rowSums(.[3:7]))

# Decompose the ECC: Beta, Lambda, and Projection Parameter
ECC_FM_PRS_Norms <- cbind(sqrt(rowSums(temp[,3:7]^2)),sqrt(rowSums(temp[,8:12]^2))) %>%
  as_tibble() %>%
  rename(Betas = V1,
         Lambdas = V2) %>%
  cbind(ECC_FM_PRS) %>%
  subset(select = c(Industry, date, ECC, Betas, Lambdas)) %>%
  mutate(PP = ECC/Betas/Lambdas,
         ECC = abs(ECC),
         PP = abs(PP)) %>%
  # transform to ln
  mutate(ECC = log(ECC),
         Betas = log(Betas)/ECC,
         Lambdas = log(Lambdas)/ECC,
         PP = log(PP)/ECC) %>%
  subset(select = - ECC) %>%
  # pivot longer
  pivot_longer(cols = c(Betas, Lambdas, PP), names_to = "Component", values_to = "Percent")

# Plot the ECC_FM_PRS
ECC_FM_PRS %>%
  mutate(date = transDate(date)) %>%
  ggplot(aes(date, ECC)) +
  geom_line() +
  scale_x_date(minor_breaks = "1 year") +
  facet_wrap(~ Industry) +
  labs(title= "Estimated Equity Cost of Capital with FM_PRS",
       x = "date") + 
  theme(plot.title = element_text(hjust=0.5),
        axis.text.x = element_text(angle = 30, hjust = 1))
```

### 5.1.4 Fama Macbeth Second Step Regression with STL Trend Data

```{r, cache = TRUE}
temp <- FM_STL_FF5
names(temp) <- tolower(names(temp))
# join the data
temp <- Port_FF5_Betas %>%
  inner_join(temp) %>%
  subset(select = -Alpha)

# Calculate the ECC 
ECC_FM_STL_FF5 <- temp[,1:2] %>%
  cbind(temp[,3:7]*temp[,8:12]) %>%
  mutate(ECC = rowSums(.[3:7]))

# Decompose the ECC: Beta, Lambda, and Projection Parameter
ECC_FM_STL_FF5_Norms <- cbind(sqrt(rowSums(temp[,3:7]^2)),sqrt(rowSums(temp[,8:12]^2))) %>%
  as_tibble() %>%
  rename(Betas = V1,
         Lambdas = V2) %>%
  cbind(ECC_FM_STL_FF5) %>%
  subset(select = c(Industry, date, ECC, Betas, Lambdas)) %>%
  mutate(PP = ECC/Betas/Lambdas,
         ECC = abs(ECC),
         PP = abs(PP)) %>%
  # transform to ln
  mutate(ECC = log(ECC),
         Betas = log(Betas)/ECC,
         Lambdas = log(Lambdas)/ECC,
         PP = log(PP)/ECC) %>%
  subset(select = - ECC) %>%
  # pivot longer
  pivot_longer(cols = c(Betas, Lambdas, PP), names_to = "Component", values_to = "Percent")

# Plot the ECC_FM_STL_FF5
ECC_FM_STL_FF5 %>%
  mutate(date = transDate(date)) %>%
  ggplot(aes(date, ECC)) +
  geom_line() +
  scale_x_date(minor_breaks = "1 year") +
  facet_wrap(~ Industry) +
  labs(title= "Estimated Equity Cost of Capital with FM_STL_FF5",
       x = "date") + 
  theme(plot.title = element_text(hjust=0.5),
        axis.text.x = element_text(angle = 30, hjust = 1))


temp <- FM_STL_PRS
names(temp) <- tolower(names(temp))
# join the data
temp <- Port_PRS_Betas %>%
  inner_join(temp) %>%
  subset(select = -Alpha)

# Calculate the ECC 
ECC_FM_STL_PRS <- temp[,1:2] %>%
  cbind(temp[,3:7]*temp[,8:12]) %>%
  mutate(ECC = rowSums(.[3:7]))

# Decompose the ECC: Beta, Lambda, and Projection Parameter
ECC_FM_STL_PRS_Norms <- cbind(sqrt(rowSums(temp[,3:7]^2)),sqrt(rowSums(temp[,8:12]^2))) %>%
  as_tibble() %>%
  rename(Betas = V1,
         Lambdas = V2) %>%
  cbind(ECC_FM_STL_PRS) %>%
  subset(select = c(Industry, date, ECC, Betas, Lambdas)) %>%
  mutate(PP = ECC/Betas/Lambdas,
         ECC = abs(ECC),
         PP = abs(PP)) %>%
  # transform to ln
  mutate(ECC = log(ECC),
         Betas = log(Betas)/ECC,
         Lambdas = log(Lambdas)/ECC,
         PP = log(PP)/ECC) %>%
  subset(select = - ECC) %>%
  # pivot longer
  pivot_longer(cols = c(Betas, Lambdas, PP), names_to = "Component", values_to = "Percent")

# Plot the ECC_FM_STL_PRS
ECC_FM_STL_PRS %>%
  mutate(date = transDate(date)) %>%
  ggplot(aes(date, ECC)) +
  geom_line() +
  scale_x_date(minor_breaks = "1 year") +
  facet_wrap(~ Industry) +
  labs(title= "Estimated Equity Cost of Capital with FM_STL_PRS",
       x = "date") + 
  theme(plot.title = element_text(hjust=0.5),
        axis.text.x = element_text(angle = 30, hjust = 1))
```

### 5.2 Decomposition of the Equity Cost of Captial

```{r, cache = TRUE}
# Plot the decomposition for ECC_AM_FF5_Norms
ECC_AM_FF5_Norms %>%
  mutate(date = transDate(date)) %>%
  ggplot(aes(date, Percent, fill = Component)) +
  geom_area() +
  scale_x_date(minor_breaks = "1 year") +
  scale_color_brewer(palette = "Paired") +
  facet_wrap(~ Industry) +
  labs(title= "Equity Cost of Capital Component Decomposition for AM_FF5",
       x = "date") + 
  theme(plot.title = element_text(hjust=0.5),
        axis.text.x = element_text(angle = 30, hjust = 1))

# Plot the decomposition for ECC_AM_PRS_Norms
ECC_AM_PRS_Norms %>%
  mutate(date = transDate(date)) %>%
  ggplot(aes(date, Percent, fill = Component)) +
  geom_area() +
  scale_x_date(minor_breaks = "1 year") +
  scale_color_brewer(palette = "Paired") +
  facet_wrap(~ Industry) +
  labs(title= "Equity Cost of Capital Component Decomposition for AM_PRS",
       x = "date") + 
  theme(plot.title = element_text(hjust=0.5),
        axis.text.x = element_text(angle = 30, hjust = 1))

# Plot the decomposition for ECC_GM_FF5_Norms
ECC_GM_FF5_Norms %>%
  mutate(date = transDate(date)) %>%
  ggplot(aes(date, Percent, fill = Component)) +
  geom_area() +
  scale_x_date(minor_breaks = "1 year") +
  scale_color_brewer(palette = "Paired") +
  facet_wrap(~ Industry) +
  labs(title= "Equity Cost of Capital Component Decomposition for GM_FF5",
       x = "date") + 
  theme(plot.title = element_text(hjust=0.5),
        axis.text.x = element_text(angle = 30, hjust = 1))

# Plot the decomposition for ECC_GM_PRS_Norms
ECC_GM_PRS_Norms %>%
  mutate(date = transDate(date)) %>%
  ggplot(aes(date, Percent, fill = Component)) +
  geom_area() +
  scale_x_date(minor_breaks = "1 year") +
  scale_color_brewer(palette = "Paired") +
  facet_wrap(~ Industry) +
  labs(title= "Equity Cost of Capital Component Decomposition for GM_PRS",
       x = "date") + 
  theme(plot.title = element_text(hjust=0.5),
        axis.text.x = element_text(angle = 30, hjust = 1))

# Plot the decomposition for ECC_FM_FF5_Norms
ECC_FM_FF5_Norms %>%
  mutate(date = transDate(date)) %>%
  ggplot(aes(date, Percent, fill = Component)) +
  geom_area() +
  scale_x_date(minor_breaks = "1 year") +
  scale_color_brewer(palette = "Paired") +
  facet_wrap(~ Industry) +
  labs(title= "Equity Cost of Capital Component Decomposition for FM_FF5",
       x = "date") + 
  theme(plot.title = element_text(hjust=0.5),
        axis.text.x = element_text(angle = 30, hjust = 1))

# Plot the decomposition for ECC_FM_PRS_Norms
ECC_FM_PRS_Norms %>%
  mutate(date = transDate(date)) %>%
  ggplot(aes(date, Percent, fill = Component)) +
  geom_area() +
  scale_x_date(minor_breaks = "1 year") +
  scale_color_brewer(palette = "Paired") +
  facet_wrap(~ Industry) +
  labs(title= "Equity Cost of Capital Component Decomposition for FM_PRS",
       x = "date") + 
  theme(plot.title = element_text(hjust=0.5),
        axis.text.x = element_text(angle = 30, hjust = 1))

# Plot the decomposition for ECC_FM_STL_FF5_Norms
ECC_FM_STL_FF5_Norms %>%
  mutate(date = transDate(date)) %>%
  ggplot(aes(date, Percent, fill = Component)) +
  geom_area() +
  scale_x_date(minor_breaks = "1 year") +
  scale_color_brewer(palette = "Paired") +
  facet_wrap(~ Industry) +
  labs(title= "Equity Cost of Capital Component Decomposition for FM_STL_FF5",
       x = "date") + 
  theme(plot.title = element_text(hjust=0.5),
        axis.text.x = element_text(angle = 30, hjust = 1))

# Plot the decomposition for ECC_FM_STL_PRS_Norms
ECC_FM_STL_PRS_Norms %>%
  mutate(date = transDate(date)) %>%
  ggplot(aes(date, Percent, fill = Component)) +
  geom_area() +
  scale_x_date(minor_breaks = "1 year") +
  scale_color_brewer(palette = "Paired") +
  facet_wrap(~ Industry) +
  labs(title= "Equity Cost of Capital Component Decomposition for FM_STL_PRS",
       x = "date") + 
  theme(plot.title = element_text(hjust=0.5),
        axis.text.x = element_text(angle = 30, hjust = 1))
```

### 5.3 Forcasting???

We can try to apply the previous methods to forecast the ECC and compare the accuracy. There is a STL method of forcasting so we might be able to use STL to forcast betas and industry risk premium and perform the second step regression to obtain the lambda. Then we can calculate the ECC.
